On Secure Delegation of SampBQP with a Classical Client

### 2020-01-21 qpip0.tex
Uncomment parallelrep 3.5
Updates from Overleaf

@@

\subsection{Subprotocol for Quantum Measurements}

We first restate the construction in \cite{mahadev_delegation}.

@@

We present a lemma from \cite{parallelrep}.

\iffalse

@@

\begin{lem}
	Let $(U_0, U)$ be some prover's strategy.
	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $i\in[m]$, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
	Let $\gamma$ be sampled uniformly from $\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document}.
	Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\psi}_{X, Z}$,

@@

\fi

\begin{lem}
	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
	Let $\gamma_i\xleftarrow{\$}\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document} for each $i\in[m]$.
	Then a state $\ket{psi}_{X, Z}$ can be partitioned as follows: \Ethan{Just gonna hard-code $c=0^m$ here for now}
	$$\ket{\psi}=\ket{\psi_0}+\ket{\psi_{10}}+\ket{\psi_{110}}+\ldots+\ket{\psi_{11\ldots10}}+\ket{\psi_{11\ldots11}}+\ket{\psi_{err}}$$
	where the way of partitioning may depend on the choices of $\hat\gamma=(\gamma_i)_{i=1}^m$.
	Furthermore, the following properties are satisfied. \Ethan{Takes a bit of parsing to see how is our case different here since $c$ might be defined differently for us}
	\begin{enumerate}
		\item stuff
		\item For any fixed $\hat\gamma$... 
		\item For any fixed $\hat\gamma$...
		\item For any fixed $c$,
			$$\E_{\hat\gamma}\left[\norm{\ket{\psi_{err}}_{X,Z}}^2\right]\leq\frac{6m^2}{T}+\negl(n)$$
		\item stuff
	\end{enumerate}
\end{lem}

>>>>

\hannote{In this section, we modify the construction of \cite{mahadev_delegation} to show that a $\QPIP_1$ protocol for $\SampBQP$ implies a $\QPIP_0$ for $\SampBQP$.}

@@

\subsection{Subprotocol for Quantum Measurements}
%\hannote{what is this for?}
As a warm-up, we  restate the construction in \cite{mahadev_delegation}, which shows that $\QPIP_1$ protocol for $\BQP$ implies a $\QPIP_0$ for $\BQP$.

@@

@@

\hannote{import 3.5. didn't import the proof, too long.}

First, We present a lemma from \cite{parallelrep}  that gives a decomposition of a cheating prover's state. We omit the proof here.

\begin{lemma}[Lemma 3.5 of \cite{parallelrep}]\label{lem:partition}
Let $(U_0,U)$ be any prover's strategy. Let $m=O(\log \secpar)$, $i\in[m]$, 
$\gamma_0 \in[0,1]$, and $T\in \mathbb{N}$ such that $\frac{\gamma_0}{T}=1/\poly(\secpar)$. Let $\gamma$ be sampled uniformly randomly from $[\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}]$. Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\psi}_{\regX,\regZ}$,  
\begin{align*}
    G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in} = z_0\ket{0^m}_{\regC}\ket{\psi_{0}}_{\regX,\regZ}\ket{0^t01}_{ph,th,in}+ z_1\ket{0^m}_{\regC}\ket{\psi_{1}}_{\regX,\regZ}\ket{0^t11}_{ph,th,in} + \ket{\psi'_{err}}
\end{align*}
where $t$ is the number of qubits in the register $ph$, $z_0,z_1\in \mathbb{C}$ such that $|z_0|=|z_1|=1$, and 
$z_0$, $z_1$, $\ket{\psi_0}_{\regX,\regZ}$, $\ket{\psi_1}_{\regX,\regZ}$, and $\ket{\psi_{err}}_{\regX,\regZ}$ may depend on $\gamma$.

Furthermore, the following properties are satisfied.
%
\begin{enumerate}
%\item There exist (sub-normalized) states $\ket{\psi_0}_{\regX,\regZ}$ and $\ket{\psi_1}_{\regX,\regZ}$ such that when $G_{i,\gamma}$ runs on input $\ket{\psi}_{\regX,\regZ}$, the output is  $(0,\ket{\psi_0}_{\regX,\regZ}/\|\ket{\psi_0}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_0}_{\regX,\regZ}\|^2$, $(1,\ket{\psi_1}_{\regX,\regZ}/\|\ket{\psi_1}_{\regX,\regZ}\|)$ with probability $\|\ket{\psi_1}_{\regX,\regZ}\|^2$, and $\bot$ with probability  $1-\|\ket{\psi_0}_{\regX,\regZ}\|^2- \|\ket{\psi_1}_{\regX,\regZ}\|^2$,
    \item If we define $\ket{\psi_{err}}_{\regX,\regZ}\defeq \ket{\psi}_{\regX,\regZ} - \ket{\psi_{0}}_{\regX,\regZ}- \ket{\psi_{1}}_{\regX,\regZ}$, then we have  $E_{\gamma}[\|\ket{\psi_{err}}_{\regX,\regZ}\|^2]\leq \frac{6}{T}+\negl(n)$.
\item For any fixed $\gamma$, $\Pr[M_{ph,th,in}\circ \ket{\psi'_{err}} \in \{0^t01,0^t11\}] =0$. %where $M_{ph,th,in}$ is the computational-basis measurement in the register $(ph,th,in)$. %and $t$ is the number of qubits in $ph$.   
This implies that if we apply the measurement $M_{ph,th,in}$ on $\frac{G_{i,\gamma} \ket{0^m}_{\regC}\ket{\psi}_{\regX,\regZ}\ket{0^t}_{ph}\ket{0}_{th}\ket{0}_{in}}{\|\ket{\psi}_{\regX,\regZ}\|}$, then the outcome is $0^tb1$ with probability $\|\ket{\psi_b}_{\regX,\regZ}\|^2$ and the resulting state in the register $(\regX,\regZ)$  is $\frac{\ket{\psi_b}_{\regX,\regZ}}{\|\ket{\psi_b}_{\regX,\regZ}\|}$ ignoring a global phase factor.
    \item For any fixed $\gamma$, $E_{b\in \{0,1\}} [\|\ket{\psi_b}_{\regX,\regZ}\|^2]\leq \frac{1}{2}\|\ket{\psi}_{\regX,\regZ}\|^2$. 
        \item 
For any fixed $\gamma$ and $c\in \bit^m$ such that $c_i=0$, we have 
\begin{align*}
\Pr\left[M_{\regX_i}\circ U\frac{\ket{c}_{\regC}\ket{\psi_0}_{\regX,\regZ}}{\|\ket{\psi_0}_{\regX,\regZ}\|}\in \Acc_{k_i,y_i}\right]\leq 2^{m-1}\gamma+\negl(\secpar).
\end{align*}
    \item 
For any fixed $\gamma$, there exists an efficient quantum algorithm $\ext_i$ such that 
\begin{align*}  
  \Pr\left[\ext_i\left(\frac{\ket{0^m}_{\regC}\ket{\psi_1}_{\regX,\regZ}}{\|\ket{\psi_1}_{\regX,\regZ}\|}\right)\in \Acc_{k_i,y_i}\right]=1-\negl(\secpar).
  \end{align*}   
\end{enumerate}
\end{lemma}

\hannote{duplicate version by ethan..}
\begin{lem}
	Let $(U_0, U)$ be some prover's strategy.
	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $i\in[m]$, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
	Let $\gamma$ be sampled uniformly from $\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document}.
	Then, there exists an efficient quantum procedure $G_{i,\gamma}$ such that for any (possibly sub-normalized) quantum state $\ket{\psi}_{X, Z}$,

@@

\Ethan{Below is 3.6. Looks kinda useful but I need to think through this $c$ thing to make sure it'll be fine even if it's not randomly generated.}
\hannote{How about include 3.6 in the theorem}

\begin{theorem}

 If there exists a $\QPIP_1$ protocol $(\bbV, \bbP)$ for $\SampBQP$ with soundness blah and completeness blah there exists a $\QPIP_0$ protocol $(\bbV', \bbP')$ for $\SampBQP$ with soundness blah' and completeness blah'

\end{theorem}
\begin{proof}
We run Mahadev's 4-round protocol \ref{} and use parallel repetition to reduce the soundness error.
\end{proof}

\begin{lem}
	Let $m=O(\log n)$ \Ethan{$n$ is problem size?}, $\gamma_0\in[0, 1]$, and $T\in\bbN$ such that $\frac{\gamma_0}{T}=\frac{1}{\poly(n)}$.
	Let $\gamma_i\xleftarrow{\$}\set{\frac{j\gamma_0}{T}}^T_{j=1}$ \Ethan{This is a set, right? Doesn't look like one in the original document} for each $i\in[m]$.
	Then a state $\ket{psi}_{X, Z}$ can be partitioned as follows: \Ethan{Just gonna hard-code $c=0^m$ here for now}
	$$\ket{\psi}=\ket{\psi_0}+\ket{\psi_{10}}+\ket{\psi_{110}}+\ldots+\ket{\psi_{11\ldots10}}+\ket{\psi_{11\ldots11}}+\ket{\psi_{err}}$$
	where the way of partitioning may depend on the choices of $\hat\gamma=(\gamma_i)_{i=1}^m$.
	Furthermore, the following properties are satisfied. \Ethan{Takes a bit of parsing to see how is our case different here since $c$ might be defined differently for us}
	\begin{enumerate}
		\item stuff
		\item For any fixed $\hat\gamma$... 
		\item For any fixed $\hat\gamma$...
		\item For any fixed $c$,
			$$\E_{\hat\gamma}\left[\norm{\ket{\psi_{err}}_{X,Z}}^2\right]\leq\frac{6m^2}{T}+\negl(n)$$
		\item stuff
	\end{enumerate}
\end{lem}
    asdf
\begin{theorem}

	Under the assumption that the learning with errors problem with superpolynomial noise ratio is computationally intractable for an efficient quantum machine, there exists a $\QPIP_0$ protocol $(\bbV, \bbP)$ for $\SampBQP$ with soundness blah and completeness blah

\end{theorem}
